Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
'-type' issue
Ok, 'they' instead of 'he/she'
But I think that here is not correct
Accepting @amorag changes and explaining about sigular they

Another important fact is that MUSES functionalities are completed by a human controller, normally the CSO, who supervises the system activity by means of a graphic interface they can interact with. Thus, adapted and inferred security rules are not directly added to the current set of rules, but they are proposed instead as draft rules to this human controller, in order to be accepted if they are interesting and useful. The system also uses the acceptance or rejection of new rules as `feedback`, learning from these decisions, and refining the rules according to this.

@@

\item The information about the user behaviour with respect to system messages, whether the users acts in consequence or against MUSES advice, as well as user feedback. The user feedback has been measured in the MUSES trials by making interviews with the people who have used MUSES, but it can also be measured by pop-up messages, such as ``has this information been useful?''-type. 
% Antonio - quito el guión porque un revisor dice que se usan demasiados y que hacen el texto menos fluído y legible.
% Paloma -  "forward slash" no significa guión. Un forward slash es un / que sí había muchos en el texto.
All this information contributes to the inference of new rules or in adaptation, in order to deal with, for instance, users that repeatedly ignored warning messages.
Moreover, important log information with regard to the parameters used or the decisions made in the different modules can be used for further tests of new inferred rules, as it is explained below.

>>>>

Another important fact is that MUSES functionalities are completed by a human controller, normally the CSO, who supervises the system activity by means of a graphic interface they can interact with. 
% Antonio - Si estamos hablando en tercera persona del singular se suele poner 'she' para referirnos a una persona de cualquier sexo, pero me gusta más poner 'he/she' para no discriminar. En todo caso intentaré poner 'they' en lugar de 'he/she', pero aquí, tal y como está redactado 'they' no queda bien por el verbo. 
% Antonio - No lo cambio porque no sé tu opinión, no es por dar trabajo extra.
% A ver, este fenómeno gramático se llama "singular they", y se considera más correcto utilizarlo que poner "he/she". No es que me lo haya inventado yo :\
Thus, adapted and inferred security rules are not directly added to the current set of rules, but they are proposed instead as draft rules to this human controller, in order to be accepted if they are interesting and useful. The system also uses the acceptance or rejection of new rules as `feedback`, learning from these decisions, and refining the rules according to this.

@@

\item The information about the user behaviour with respect to system messages, whether the users acts in consequence or against MUSES advice, as well as user feedback. The user feedback has been measured in the MUSES trials by making interviews with the people who have used MUSES, but it can also be measured by pop-up messages, such as ``has this information been useful?''. 
% Antonio - quito el guión porque un revisor dice que se usan demasiados y que hacen el texto menos fluído y legible.
% Paloma -  "forward slash" no significa guión. Un forward slash es un / que sí había muchos en el texto.
% Antonio- Ok. En todo caso lo dejaría sin el '-type', pero como veas. Si lo quieres poner como estaba, el ', such as' lo añadí yo y lo mismo no queda bien así. 
% Ok pues con el such as.
All this information contributes to the inference of new rules or in adaptation, in order to deal with, for instance, users that repeatedly ignored warning messages.
Moreover, important log information with regard to the parameters used or the decisions made in the different modules can be used for further tests of new inferred rules, as it is explained below.
